Comparative study of requantization of time-dependent mean-field for pairing dynamics

### 2017-10-31 draft1.1.tex
removed adiabatic approximation, changed IV C

In principle, the TDHFB dynamics can be large amplitude motion.
The problem is that it is not easy to determine quantum mechanical 
quantities, such as energy eigenvalues and transition matrix elements,
from the TDHFB trajectories.
For this purpose,
since the TDHF(B) trajectory corresponds to a classical limit of the path
integral formulation,
the requantization of the mean-field dynamics was
proposed \cite{Neg80,path,path2,Rei80}.
It recovers quantum fluctuations missing in the mean-field
level, and possibly enables us to describe large-amplitude collective
tunneling phenomena such as spontaneous fission \cite{Neg80}.
The requantization of the TDHFB is particularly feasible
for integrable systems, because the system is described by separable
action-angle variables $(I_k, \phi_k)$, leading to
the Einstein-Brillouin-Keller (EBK) quantization condition.
However, for nonintegrable systems in general, it is difficult to find
suitable periodic orbits to quantize.
A possible solution to this difficulty is to find a decoupled collective
subspace spanned by
a single coordinate and its conjugate momentum \cite{NMMY16}.
Since the one-dimensional system is integrable, the quantization is
practicable.

@@

The energy eigenstates correspond to stationary states,
$\braket{Z|\psi(t)} \propto \braket{Z|\psi(0)}=\psi(Z)$,
which can be constructed by superposing the coherent states along
a periodic TDHFB trajectory $Z_{\rm cl}^{(k)}$ as \cite{path,path2,SM88}.
\begin{equation}
	\ket{\phi_k} = \oint d\mu(Z_{\rm cl}^{(k)}) \ket{Z_{\rm cl}^{(k)}}
	e^{i\mathcal{T}[Z_{\rm cl}^{(k)}]} .
\end{equation}
The single-valuedness of the wave function leads to
the quantization condition ($k$: integer)
\begin{equation}
	\mathcal{T}_\circ[Z_{\rm cl}^{(k)}]=
	\oint \frac{i}{2} \sum_l \frac{\Omega_l}{1+|Z_l^{(k)}|^2}
	\left(Z_l^{(k)*} dZ_l^{(k)} - Z_l^{(k)} dZ_l^{(k)*}\right) = 2k\pi .
	\label{EBK}
\end{equation}
The state evolves in time as $\ket{\phi(t)}=\ket{\phi}e^{-iE_k t}$,
with the energy of the $k$-th periodic trajectory,
$E_k=\mathcal{H}(Z_{\rm cl}^{(k)},Z_{\rm cl}^{(k)*})$.

@@

The most common approach to the quantization of the nuclear collective model
is the canonical quantization \cite{BM75}.
In the pairing collective model, the canonical quantization
was adopted in previous studies \cite{BBPK70,delta1,delta3}.
Assuming magnitude and phase of the pairing gap as collective coordinates,
a collective Hamiltonian was constructed in the second order in momenta.
Then, the Hamiltonian was quantized by the canonical quantization
with the Pauli's prescription.
In this section, we apply similar quantization method to
the TDHFB Hamiltonian (\ref{TDHFB_Hamiltonian_3}).
The main difference is that the collective canonical variables are
not assumed in the present case, but are obtained from the TDHFB dynamics
itself.\par
In this section, we consider two separated methods to solve the quantum mechanics: periodic boundary condition and adiabatic approximation. 
%The most natural procedure for quantizing classical dynamics is canonical quantization. The canonical variables become to operators and fulfill the commutation relation

\subsubsection{Periodic boundary condition}
\label{subsec:canonical1}

@@

@@

We assume $j$ as a coordinate, $\phi$ as a conjugate momentum. 
The adiabatic approximation means $\phi$ in Hamiltonian can be
 expanded up to second order
\begin{align}
 \mathcal{H}(\phi,j;J)
	\approx V(j:J) + \frac{1}{2B(j;J)}j^2
\end{align}
where
\begin{align}
 V(j:J) &\equiv \mathcal{H}(\phi=0,j;J) \nonumber \\
  &= \sum_{l=1,2} \Omega_l \left\{ \epsilon_l(1- q_l)
	- \frac{g}{4} (\Omega_l(1-q_l^2)+(1-q_l)^2) \right\}
- \frac{g}{2}\Omega_1\Omega_2
	\sqrt{(1-q_1^2)(1-q_2^2)} \\
 B(j;J)^{-1} &\equiv \left. \frac{\partial^2\mathcal{H}}{\partial\phi^2}\right|_{\phi=0} \nonumber \\
 &= \frac{g}{2}\Omega_1\Omega_2
	\sqrt{(1-q_1^2)(1-q_2^2)} .
\end{align}
We transform the carved space into plain space
 which keeps the mass parameter equals one
\begin{align}
 \mathcal{H}(\phi,j;J) \to \mathcal{\bar{H}}(p,q;J) = \bar{V}(q;J) + \frac{1}{2}p^2 .
\end{align}
The relation between both coordinates fulfills
\begin{align}
 \frac{\partial q(j)}{\partial j} = \sqrt{B(j;J)} .
\end{align}
Instead of Pauli prescription, we solve the Schr\"{o}dinger equation in plain space
\begin{equation}
	\bar{H}\left( q,-i\frac{d}{dq},\frac{N}{2} \right)
	u_k^{(N)}(q) = E_k^{(N)}u_k^{(N)}(q).
	\label{Schroedinger_eq2}
\end{equation}
At weak pairing limit in ground state, most of the component of wave function is expected to occupy around the minimum value of $j$. We choose Neumann boundary condition $u_k^{(N)}(q)'|_{q=q_{min}}=0$, where $q_{min}$ corresponds to the minimum value of $j$.

@@

We apply the requantization methods in Sec.~\ref{sec:requantization}.
In the following, the stationary-phase approximation to the path
integral in Sec.~\ref{sec:SPA} is denoted as ``SPA'',
the Fourier decomposition method (Sec.~\ref{sec:Fourier}) as ``FD'',
 the canonical quantization with periodic boundary condition 
(Sec.~\ref{subsec:canonical1}) as ``CQ1'', and the canonical quantization 
with adiabatic approximation (Sec.~\ref{subsec:canonical2})  as ``CQ2''.
In addition, the harmonic approximation at the ground state is
called ''HA''.
Note that the SPA and the FD produce the same eigenenergies which
are based on the EBK quantization rule.

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{images/N50ex_energy2.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=50$ system.}
 \label{fig:N50energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=50$ system. The upper and lower panels display the results for $x=0.5$ and $x=2$, respectively. From (\ref{momentum}), $j=-12.5$ corresponds to 0p50h configuration, $j=-11.5$ corresponds to 2p52h configuration, and so on.}
 \label{fig:N50_occ}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{images/N100ex_energy2.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=100$ system.}
 \label{fig:N100energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N100Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=100$ system. The upper and lower panels display the results for $x=0.5$ and $x=2$, respectively. From (\ref{momentum}), $j=-25$ corresponds to 0p0h configuration, $j=-24$ corresponds to 2p2h configuration, and so on.}
 \label{fig:N100_occ}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{images/N8ex_energy2.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=8$ system.}
 \label{fig:N8energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N8Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N8Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=8$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From (\ref{momentum}), $j=-2$ corresponds to 0p8h configuration, $j=-1$ corresponds to 2p10h configuration, and so on.}
 \label{fig:N8_occ}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{images/N16ex_energy2.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=16$ system.}
 \label{fig:N16energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N16Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N16Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=16$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively.From (\ref{momentum}), $-4$ corresponds to 0p0h configuration, $-3$ corresponds to 2p2h configuration, and so on.}
 \label{fig:N16_occ}
\end{figure}

@@

In the superfluid phase, the energy minimization always lead to $\phi=0$.
Although the global gauge angle $\Phi$ is arbitrary,
the deformation parameter $\alpha$ in gauge space is usually taken as real value ($\Phi=0$).
\begin{align}
\alpha(j,J) = \braket{Z_0|\hat{S}_-|Z_0} %= g\sum_{k>0} u_kv_k \nonumber \\
	= \sum_{l=1}^2 S_l\sqrt{1-q_l^2} . % = \Delta(\pi) .
 \label{Delta_BCS}
\end{align}
The relation between $j$ and $\alpha$ 
and that between $j$ and $E=\mathcal{H}(\phi=0,j;J)$
are shown for $\Omega=8$
in Figs. \ref{fig:p_Delta1} ($N=8$) and \ref{p_Delta2} ($N=16$).
%These results correspond to the system in Section 4.2. 
The deformation parameter $\alpha$ is largest at $j=0$ (equal filling in both levels),
and smallest at end points of $j$.
The constrained minimization with respect to $\alpha$ cannot 
produce the states corresponding to $j>0$.
Apparently, we cannot map the entire region of $j$ to $\alpha$,
since there is no one-to-one correspondence between $j$ and $\alpha$.

If the system has a deep potential at $j<0$ to prevent the wave function
from spreading toward the region of $j<0$,
we may justify the use of $\alpha$ as a coordinate in
the collective model.
For very large $\Omega$, this is the case.
However, for $\Omega=8$, the treatment can be justified only for
a very limited region of $x$, namely in the weak pairing limit.
For instance, we show the potential energy curves as functions of $\alpha$
in Fig.~\ref{fig:Delta_E} for the $N=16$ case.
In the weak pairing case ($x=0.5$),
assuming the Neumann boundary condition at $\alpha=0$,
we may obtain the colletive wave functions up to the third excited states.
On the other hand, in the strong pairing case ($x=3.2$), 
even the ground state may not be bound in the region of $j<0$.

@@

\begin{figure}[htbp]
 \begin{minipage}{0.45\hsize}
 \begin{center}
  \includegraphics[width=130mm,angle=-90]{images/N50gap_E.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{0.45\hsize}
 \begin{center}
  \includegraphics[width=130mm,angle=-90]{images/N16gap_E.eps}
 \end{center}
\end{minipage}
 \caption{Energy surface with respect to $\alpha$ in $x=0.5$, $x=1$ and $x=2$. 
Green lines are energy spectra until 3rd excitation obtained from CQ2 
(Sec.~\ref{subsec:canonical2}). Left panels: $\Omega=50$, $N=50$ system;
 Right panels: $\Omega=8$, $N=16$ system.}
 \label{fig:Delta_E}
\end{figure}

@@

\section{Conclusion}

>>>>

In principle, the TDHFB dynamics can be large amplitude motion.
The problem is that it is not easy to determine quantum mechanical 
quantities, such as energy eigenvalues and transition matrix elements,
from the TDHFB trajectories.
For this purpose,
since the TDHF(B) trajectory corresponds to a classical limit of the path
integral formulation,
the requantization of the mean-field dynamics was
proposed \cite{Neg80,KS80,K81,Rei80}.
It recovers quantum fluctuations missing in the mean-field
level, and possibly enables us to describe large-amplitude collective
tunneling phenomena such as spontaneous fission \cite{Neg80}.
The requantization of the TDHFB is particularly feasible
for integrable systems, because the system is described by separable
action-angle variables $(I_k, \phi_k)$, leading to
the Einstein-Brillouin-Keller (EBK) quantization condition.
However, for nonintegrable systems in general, it is difficult to find
suitable periodic orbits to quantize.
A possible solution to this difficulty is to find a decoupled collective
subspace spanned by
a single coordinate and its conjugate momentum \cite{NMMY16}.
Since the one-dimensional system is integrable, the quantization is
practicable.

@@

The energy eigenstates correspond to stationary states,
$\braket{Z|\psi(t)} \propto \braket{Z|\psi(0)}=\psi(Z)$,
which can be constructed by superposing the coherent states along
a periodic TDHFB trajectory $Z_{\rm cl}^{(k)}$ as \cite{KS80,K81,SM88}.
\begin{equation}
	\ket{\phi_k} = \oint d\mu(Z_{\rm cl}^{(k)}) \ket{Z_{\rm cl}^{(k)}}
	e^{i\mathcal{T}[Z_{\rm cl}^{(k)}]} .
\end{equation}
The single-valuedness of the wave function leads to
the quantization condition ($k$: integer)
\begin{equation}
	\mathcal{T}_\circ[Z_{\rm cl}^{(k)}]=
	\oint \frac{i}{2} \sum_l \frac{\Omega_l}{1+|Z_l^{(k)}|^2}
	\left(Z_l^{(k)*} dZ_l^{(k)} - Z_l^{(k)} dZ_l^{(k)*}\right) = 2k\pi .
	\label{EBK}
\end{equation}
The state evolves in time as $\ket{\phi(t)}=\ket{\phi}e^{-iE_k t}$,
with the energy of the $k$-th periodic trajectory,
$E_k=\mathcal{H}(Z_{\rm cl}^{(k)},Z_{\rm cl}^{(k)*})$.

@@

The most common approach to the quantization of the nuclear collective model
is the canonical quantization \cite{BM75}.
In the pairing collective model, the canonical quantization
was adopted in previous studies \cite{BBPK70,delta1,delta3}.
Assuming magnitude and phase of the pairing gap as collective coordinates,
a collective Hamiltonian was constructed in the second order in momenta.
Then, the Hamiltonian was quantized by the canonical quantization
with the Pauli's prescription.
In this section, we apply similar quantization method to
the TDHFB Hamiltonian (\ref{TDHFB_Hamiltonian_3}).
The main difference is that the collective canonical variables are
not assumed in the present case, but are obtained from the TDHFB dynamics
itself.\par

%In this section, we consider two separated methods to solve the quantum mechanics: periodic boundary condition and adiabatic approximation. 
%The most natural procedure for quantizing classical dynamics is canonical quantization. The canonical variables become to operators and fulfill the commutation relation

%\subsubsection{Periodic boundary condition}
%\label{subsec:canonical1}

@@

\begin{comment}

@@

We hope that the pairing large amplitude collective motion can be 
described in adiabatic approximation. 
We assume $j$ as a coordinate, $\phi$ as a conjugate momentum. 
The adiabatic approximation means the conjugate momentum in Hamiltonian can be
 expanded up to second order
\begin{align}
 \mathcal{H}(\phi,j;J)
	\approx V(j:J) + \frac{1}{2B(j;J)}\phi^2
\end{align}
where
\begin{align}
 V(j:J) &\equiv \mathcal{H}(\phi=0,j;J) \nonumber \\
  &= \sum_{l=1,2} \Omega_l \left\{ \epsilon_l(1- q_l)
	- \frac{g}{4} (\Omega_l(1-q_l^2)+(1-q_l)^2) \right\}
- \frac{g}{2}\Omega_1\Omega_2
	\sqrt{(1-q_1^2)(1-q_2^2)} \\
 B(j;J)^{-1} &\equiv \left. \frac{\partial^2\mathcal{H}}{\partial\phi^2}\right|_{\phi=0} \nonumber \\
 &= \frac{g}{2}\Omega_1\Omega_2
	\sqrt{(1-q_1^2)(1-q_2^2)} .
\end{align}
Because $B(j;J)$ diverges at both end points in $j$ space, it has advantage 
to transform the carved space into plain space which keeps the mass parameter equals one
\begin{align}
 \mathcal{H}(\phi,j;J) \to \mathcal{\bar{H}}(p,q;J) = \bar{V}(q;J) + \frac{1}{2}p^2 .
\end{align}
The relation between both coordinate systems fulfills
\begin{align}
 \frac{\partial q(j)}{\partial j} = \sqrt{B(j;J)} .
\end{align}
Instead of Pauli prescription, we solve the Schr\"{o}dinger equation in plain space
\begin{equation}
	\bar{H}\left( q,-i\frac{d}{dq},\frac{N}{2} \right)
	u_k^{(N)}(q) = E_k^{(N)}u_k^{(N)}(q).
	\label{Schroedinger_eq2}
\end{equation}
At weak pairing ($x<1$) in ground state, most of the component of wave function is 
expected to occupy around the minimum value of $j$. 
We choose Neumann boundary condition $u_k^{(N)}(q)'|_{q=q_{min}}=0$, 
where $q_{min}$ corresponds to the minimum value of $j$. Under such boundary condition, 
the occupation probability in $j$ space approaches to $\delta(j)$ in $x\to 0$ limit.

\end{comment}

@@

We apply the requantization methods in Sec.~\ref{sec:requantization}.
In the following, the stationary-phase approximation to the path
integral in Sec.~\ref{sec:SPA} is denoted as ``SPA'',
the Fourier decomposition method (Sec.~\ref{sec:Fourier}) as ``FD'',
and the canonical quantization with periodic boundary condition 
(Sec.~\ref{subsec:canonical1}) as ``CQ''.
%In addition, the harmonic approximation at the ground state is called ''HA''.
Note that the SPA and the FD produce the same eigenenergies which
are based on the EBK quantization rule.

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{images/N50ex_energy_wo_adiabatic.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=50$ system.}
 \label{fig:N50energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=50$ system. The upper and lower panels display the results for $x=0.5$ and $x=2$, respectively. From (\ref{momentum}), $j=-12.5$ corresponds to 0p50h configuration, $j=-11.5$ corresponds to 2p52h configuration, and so on.}
 \label{fig:N50_occ}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{images/N100ex_energy_wo_adiabatic.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=100$ system.}
 \label{fig:N100energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N100Xeq0p5occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=100$ system. The upper and lower panels display the results for $x=0.5$ and $x=2$, respectively. From (\ref{momentum}), $j=-25$ corresponds to 0p0h configuration, $j=-24$ corresponds to 2p2h configuration, and so on.}
 \label{fig:N100_occ}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{images/N8ex_energy_wo_adiabatic.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=8$ system.}
 \label{fig:N8energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N8Xeq0p5occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N8Xeq2occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=8$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From (\ref{momentum}), $j=-2$ corresponds to 0p8h configuration, $j=-1$ corresponds to 2p10h configuration, and so on.}
 \label{fig:N8_occ}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{images/N16ex_energy_wo_adiabatic.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=16$ system.}
 \label{fig:N16energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N16Xeq0p5occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N16Xeq2occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=16$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively.From (\ref{momentum}), $-4$ corresponds to 0p0h configuration, $-3$ corresponds to 2p2h configuration, and so on.}
 \label{fig:N16_occ}
\end{figure}

@@

In the superfluid phase, the energy minimization always lead to $\phi=0$.
Although the global gauge angle $\Phi$ is arbitrary,
the deformation parameter $\alpha$ in gauge space is usually taken as real value ($\Phi=0$).
\begin{align}
\alpha(j,J) = \braket{Z_0|\hat{S}_-|Z_0} %= g\sum_{k>0} u_kv_k \nonumber \\
	= \sum_{l=1}^2 S_l\sqrt{1-q_l^2} . % = \Delta(\pi) .
 \label{Delta_BCS}
\end{align}
Using $\alpha$ as a coordinate is equivalent to using pairing gap $\Delta$ as a coordinate because the relation
\begin{align}
  \alpha = \frac{1}{2}\sum_{k>0}\frac{\Delta}{\sqrt{(\epsilon_k-\lambda)^2+\Delta^2}}
\end{align}
guarantees one-to-one correspondence between $\alpha$ and $\Delta$.
The relation between $j$ and $\alpha$ 
and that between $j$ and $E=\mathcal{H}(\phi=0,j;J)$
are shown for $\Omega=8$
in Fig. \ref{fig:p_Delta1} ($N=8$) and Fig. \ref{fig:p_Delta2} ($N=16$).
%These results correspond to the system in Section 4.2. 
The deformation parameter $\alpha$ is largest at $j=0$ (equal filling in both levels),
and smallest at end points of $j$.
The constrained minimization with respect to $\alpha$ cannot 
produce the states corresponding to $j>0$.
Apparently, we cannot map the entire region of $j$ to $\alpha$,
since there is no one-to-one correspondence between $j$ and $\alpha$.

If the system has a deep potential at $j<0$ to prevent the wave function
from spreading toward the region of $j<0$,
we may justify the use of $\alpha$ as a coordinate in
the collective model.
For very large $\Omega$, this is the case (See Fig. \ref{fig:Delta_E}, left panels).
However, for $\Omega=8$, the treatment can be justified only for
a very limited region of $x$, namely in the weak pairing limit.
For instance, we show the potential energy curves as functions of $\alpha$
in Fig.~\ref{fig:Delta_E} for the $N=16$ case.
In the weak pairing case ($x=0.5$),
assuming the Neumann boundary condition at $\alpha=0$,
we may obtain the colletive wave functions up to the third excited states.
On the other hand, in the strong pairing case ($x=3.2$), 
even the ground state may not be bound in the region of $j<0$.

@@

\begin{figure}[htbp]
 \begin{minipage}{0.45\hsize}
 \begin{center}
  \includegraphics[width=50mm,angle=-90]{images/N50Xeq2p4gap_E.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{0.45\hsize}
 \begin{center}
  \includegraphics[width=50mm,angle=-90]{images/N16Xeq2p4gap_E.eps}
 \end{center}
\end{minipage}
 \caption{Energy surface with respect to $\alpha$ in $x=2.4$. 
Green lines are energy spectra until 3rd excitation obtained from CQ 
(Sec.~\ref{sec:canonical}). Left panels: $\Omega=50$, $N=50$ system;
 Right panels: $\Omega=8$, $N=16$ system.}
 \label{fig:Delta_E}
\end{figure}

@@

\section{Conclusion}
\label{sec:conclusion}
